Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-20 ba_resubmit/rebuttal/response.tex

\setcounter{responsectr}{0}
\section{Reviewer Comments}

	\pointRaised{R}{%
	For the missing data treatment now included just before Section 2.1, is the assumption truly missing at random, or missing completely at random? Or, does this distinction not matter because of the independence assumed across elements of the comparison vector?}

	\reply{\textcolor{teal}{The distinction does not matter due to assuming that the comparison vectors are conditionally independent given the coreference matrix (or matching label). We now state the following in Section 3, page 5:}

	\textcolor{teal}{``\textcolor{teal}{We now explain how we accommodate missing fields, which leads to missing comparison vectors. To denote a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are missing at random (MAR) or missing completely at random (MCAR). It is important to note that for likelihood based inference, both MAR and MCAR lead to ignorability, or rather, being able to consider the likelihood for the observed data \citep[Section 6.2]{LittleRubin2002}. Therefore, we can marginalize over the missing data and perform all computation using the observed data, leading to (6a). For further details on these connections, refer to \cite[Section 6.2]{LittleRubin2002}, \cite[Section 3.1]{sadinle_detecting_2014}, and \citep[Section 4.2]{sadinle_bayesian_2017}}."}
	}

### 2023-07-20 ba_resubmit/kundinger_final.tex
done with pass. sent to jerry and brian.

\textcolor{teal}{We now explain how we accommodate missing fields, which leads to missing comparison vectors. To denote a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are missing at random (MAR) or missing completely at random (MCAR). It is important to note that for likelihood based inference, both MAR and MCAR lead to ignorability, or rather, being able to consider the likelihood for the observed data \citep[Section 6.2]{LittleRubin2002}. Therefore, we can marginalize over the missing data in (\ref{eqn:likelihood}) and perform all computation using the observed data. For details, refer to \cite[Section 6.2]{LittleRubin2002}, \cite[Section 3.1]{sadinle_detecting_2014}, and \citep[Section 4.2]{sadinle_bayesian_2017}.
}

>>>>

\textcolor{red}{Jerry: could you read through this carefully please regarding the missing data part? Note: we only give the marginalized likelihood and not the likelihood without the missing data.}

\textcolor{teal}{We now explain how we accommodate missing fields, which leads to missing comparison vectors. To denote a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. Assume the comparison vectors are conditionally independent given the coreference matrix (or matching label) and that missing comparisons are missing at random (MAR) or missing completely at random (MCAR). It is important to note that for likelihood based inference, both MAR and MCAR lead to ignorability, or rather, being able to consider the likelihood for the observed data \citep[Section 6.2]{LittleRubin2002}. Therefore, we can marginalize over the missing data and perform all computation using the observed data, leading to (\ref{eqn:likelihood}). For further details on these connections, refer to \cite[Section 6.2]{LittleRubin2002}, \cite[Section 3.1]{sadinle_detecting_2014}, and \citep[Section 4.2]{sadinle_bayesian_2017}.
}
